---
title: "RegresionesGrupo4"
author: "Esdras Sosof"
date: "2024-03-16"
output: html_document
---
#Ejemplo an치lisis de datos. BDD Advertising
#><
```{r}
base_de_datos<-read.csv("Advertising.csv", sep=",")
base_de_datos
```
```{r}
str(base_de_datos)
summary(base_de_datos)
```
#llamar librerias
```{r}
library(dplyr)
library(ggplot2)
library(PerformanceAnalytics)
```

```{r}
chart.Correlation(base_de_datos)
```
```{r}
base_de_datos %>%
  ggplot(aes(x=TV,y=Sales))+
  geom_point(col='blue')+
  geom_smooth(method="lm", se=FALSE)+
  theme_minimal()
```
```{r}
base_de_datos %>%
  ggplot(aes(x=Newspaper,y=Sales))+
  geom_point(col='blue')+
  geom_smooth(method="lm", se=FALSE)+
  theme_minimal()
```
```{r}
base_de_datos %>%
  ggplot(aes(x=Radio,y=Sales))+
  geom_point(col='blue')+
  geom_smooth(method="lm", se=FALSE)+
  theme_minimal()
```
#Construcci칩n de un modelo
```{r}
lm1<-base_de_datos %>%
  lm(formula= Sales ~ TV)
lm1
```
```{r}
lm2<-base_de_datos %>%
  lm(formula= Sales ~ Radio)
lm2
```
```{r}
lm3<-base_de_datos %>%
  lm(formula= Sales ~ Newspaper)
lm3
```
#Pr치ctica de predicci칩n
```{r}
predict(object = lm1, newdata = data.frame(TV=c(200)))
```

library(ggplot2)
ggplot(dataset, aes(TV,Sales))+
geom_point(col="steelbue")+
geom_smooth(method="lm", se=False, col="red")
